\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-22 papers/jss/article.Rnw
Remove the wooden 30-day qualifier about active users.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@820 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than 300 30-day active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.

>>>>

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the R system with the ability to create, read and write Protocol
Buffer message. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts and software engineers.
At the time of this writing there are more than 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with other distributed systems written in C++, Java, Python, and 
other languages.
